\documentclass[12pt]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{sectsty}
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{dsfont}

\sectionfont{\fontsize{12}{12}\selectfont}
\subsectionfont{\fontsize{12}{12}\selectfont}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

\begin{document}

\title{Assignment 1: Sets}
\author{Declan Murphy Zink}
\date{9/10/2020}

\maketitle

\section{
    Let A be the set $\{\alpha,\{1,\alpha\},\{3\},\{\{1,3\}\},3\}.$ 
    Which of the following statements are true and which are false?
}
\subsection{$\alpha \in A.$}
true
\subsection{$\{\alpha\} \notin A.$}
true
\subsection{$\{1,\alpha\} \subseteq A.$}
false
\subsection{$\{3,\{3\}\} \subseteq A.$}
true
\subsection{$\{1,3\} \in A.$}
false
\subsection{$\{\{1,3\}\} \subseteq A.$}
false
\subsection{$\{\{1,\alpha\}\} \subseteq A.$}
true
\subsection{$\{1,\alpha\} \notin A.$}
false
\subsection{$\emptyset \subseteq A.$}
true

\section{
    Let B,C,D,E be the following sets:
}
\begin{gather*}
    B = \{x|x$ a real number$,x^2 < 4\},\\
    C = \{x|x$ a real number$, 0 <= x < 2\},\\
    D = \{x|x \in \mathds{Z} ,x^2 < 1\},\\
    E = \{1\}.
\end{gather*}
\subsection{Which pair of these sets has the property that neither is contained in the other?}
Sets D and E
\subsection{
    You are given that X is one of the sets B,C,D,E, but you do not know which one.
    You are also given that $E \subseteq X$ and $X \subseteq B$. What can you deduce about X?
}
X is either B or E\\\\

\section{
    Which of the following arguments are valid?
    For the valid ones, write down the argument symbolically.
}
\subsection{
    I eat chocolate if I am depressed.
    I am not depressed.
    Therefore I am not eating chocolate.
}
Not valid
\subsection{
    I eat chocolate only if I am depressed.
    I am not depressed.
    Therefore I am not eating chocolate.
}
Valid. If C is eating chocolate and D is being depressed, then $P \Leftrightarrow D$, so $\bar{P} \Leftrightarrow \bar{D}$.
\subsection{
    If a movie is not worth seeing, then it was not made in England.
    A movie is worth seeing only if critic Ivor Smallbrain reviews it.
    The movie \emph{Cat on a Hot Tin Proof} was not reviewed by Ivor Smallbrain.
    Therefore \emph{Cat on a Hot Tin Proof} was not made in England.
}
Valid. If W is worth seeing, E is made in England, and I is reviewed by Ivor Smallbrain, 
then $\bar{W} \Rightarrow \bar{E}$ and $W \Leftrightarrow I$.
Therefore $\bar{I} \Leftrightarrow \bar{W}$ and then $\bar{I} \Rightarrow \bar{E}$.
\end{document}